Arrangement for DroneGo

### 2020-03-09 PAPER.tex
Updates from Overleaf

    $c_0$    & The initial CO$_2$ concentration(in 1850) \\
    $F(t)$  & radiative forcing in year t \\
    $a_0,b$  & \textcolor[rgb]{ .133,  .133,  .133}{Constant coefficient} \\
    $T(t)$  & \textcolor[rgb]{ .2,  .2,  .2}{Temperature in year t} \\
    $\beta$  & Specific heat capacity \\
    $\gamma$ & heat capacity ratio  \\
    $\kappa$ & \multicolumn{1}{p{25.555em}}{thermal diffusion coefficient of ocean} \\
    $LCI$   & Liveable Country Index \\
    $NRI$   & \textcolor[rgb]{ .133,  .133,  .133}{National Responsibility Index} \\
    $IRI$   & International Responsibility Index \\
    \toprule
    \end{tabular}%
  \label{Notations}%
\end{table}%

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture 3 levels.png}
	\caption{ Preservation Policy of Culture}\label{culture 3 levels}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{LCI.png}
	\caption{ Countries with eligible immigration indices }\label{Countries_with_eligible_immigration_indices}
\end{figure}

@@

\newpage
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{NRI.png}
	\caption{ International Responsibility Index}\label{NRI}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{IRI.png}
	\caption{ Country Index}\label{country_index}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{high_index_countries.png}
	\caption{High-index Countries}\label{high_index_countries}
\end{figure}

@@

%-------------------------------------8
\section{Migration Policy Based on Protection of Human Rights}

@@

% 参考文献，此处以 MLA 引用格式为例
\begin{thebibliography}{99}
\bibitem{1} Einstein, A., Podolsky, B., \& Rosen, N. (1935). Can quantum-mechanical description of physical reality be considered complete?. \emph{Physical review}, 47(10), 777.
\bibitem{2} \emph{A simple, easy \LaTeX\ template for MCM/ICM: EasyMCM}. (2018). Retrieved December 1, 2019, from\url{https://www.cnblogs.com/xjtu-blacksmith/p/easymcm.html}
\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

    $c_0$    & The initial CO$_2$ concentration(in 1850) \\
    $F(t)$  & radiative forcing in year t \\
    $a_0,b$  & \textcolor[rgb]{ .133,  .133,  .133}{Constant coefficient} \\
    $T(t)$  & \textcolor[rgb]{ .2,  .2,  .2}{Temperature in year t} \\
    $\beta$  & Specific heat capacity \\
    $\gamma$ & heat capacity ratio  \\
    $\kappa$ & \multicolumn{1}{p{25.555em}}{thermal diffusion coefficient of ocean} \\
    LCI   & Liveable Country Index \\
    NRI   & \textcolor[rgb]{ .133,  .133,  .133}{National Responsibility Index} \\
    IRI   & International Responsibility Index \\
    \toprule
    \end{tabular}%
  \label{Notations}%
\end{table}%

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture 3 levels.png}
	\caption{ Three levels of culture protection }\label{culture 3 levels}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{LCI.png}
	\caption{ Countries with the LCI greater than 0 }
	\label{Countries_with_eligible_immigration_indices}
\end{figure}

@@

\newpage
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{NRI.png}
	\caption{ The NRI of 57 countries}\label{NRI}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{IRI.png}
	\caption{ The IRI of 57 countries}\label{country_index}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{high_index_countries.png}
	\caption{Countries with an IRI greater than 0.3}\label{high_index_countries}
\end{figure}

@@

%-------------------------------------8
\section{Migration Policy Based on Protection of Human Rights}
With the support of the above model, we developed an immigration policy that fully protects the EDPs' human rights, as shown below：

1. \textbf{UN should make accurate statistics of country data for calculation of the Comprehensive Index}, for the island countries in different geographical locations to choose the suitable host country. The Composite Index of island countries in one of six sea regions varies with different host countries. Depending on the difference in the Composite Index, host countries may accept the EDPs from the same sea region in proportion to the Composite Index. This would be fairer to the host countries and would not result in a large number of EDPs crowding in one host country.

2. \textbf{Establish a special international relief fund for climate refugees}. The money should come from developed countries that are mainly responsible for climate change, with some earmarked for climate refugees. The division of responsibility is demanding. So we determine each country's "national responsibility index" based on its CO2 emissions and per capita energy consumption. The larger the index, the higher the country's responsibility for global climate change, to determine which countries are obliged to participate in the financing and the proportion of financing.

@@

% 参考文献，此处以 MLA 引用格式为例
\begin{thebibliography}{99}
\bibitem{1} Einstein, A., Podolsky, B., \& Rosen, N. (1935). Can quantum-mechanical description of physical reality be considered complete?. \emph{Physical review}, 47(10), 777.
\bibitem{2} \emph{A simple, easy \LaTeX\ template for MCM/ICM: EasyMCM}. (2018). Retrieved December 1, 2019, from\url{https://www.cnblogs.com/xjtu-blacksmith/p/easymcm.html}

\bibitem{3} Wigley, T., Schlesinger, M. Analytical solution for the effect of increasing CO$_2$ on global mean temperature. \emph{Nature} 315, 649–652 (1985). \url{https://doi.org/10.1038/315649a0}

\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
